---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# xkcd

<!-- badges: start -->
<!-- badges: end -->

The `xckd` package provides an R interface to retrieve data about [xkcd comics](https://xkcd.com/) from the xkcd website - and most importantly, view those comics in your plot window!

## Installation

You can install the development version of xkcd from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("wjhopper/xkcd")
```

## Browsing comics

Given a comic number, the `xkcd()` function retrieves a JSON object with metadata about that comic.

```{r example}
library(xkcd)

# Retrieve data about the first xkcd comic ever!
first_comic <- xkcd(1)
first_comic
```

The most useful thing you can do with these objects is plot them, which displays the comic image in your plot window.

```{r}
plot(first_comic)
```

## Comic Data
The metadata from all 2,850 xkcd comics (so far) is aggregated into the `xkcd_data` data set 

```{r}
head(xkcd_data)
```
