---
title: "Using the xkcd package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the xkcd package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Browsing xkcd comics 

The main function of the xkcd package is to let you browse xkcd comics from with in R. Let's see how we can accomplish this. First, load the `xkcd` package.

```{r setup}
library(xkcd)
```

Then, use the `xkcd()` function to retreive information about a particular comics. We'll retrieve information about the very first xkcd comics, so we'll set the `number` argument equal to 1

```{r}
comic <- xkcd(number = 1)
```

The objects returned by the `xkcd()` function are special lists that belong to the xkcd class. This is useful because they can be provided directly to the `plot()` function in order to display the comic

```{r}
plot(comic)
```

## Comic Data
The xkcd package also comes with a built-in data set describing the first 10 xkcd comics ever published

```{r}
xkcd::xkcd_data
```




















